### 2018-06-17 tex/manuscript.tex
rough draft intro

		As a weevil (snout beetle), members of the genus \textit{Curculio} are typified by the presence of a highly elongate structure on the head, called the rostrum (snout). 
		This structure is a hollow, cylindrical extension of the exoskeleton of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts. 
		The space inside of the rostrum contains the esophagus, various muscles and tendons used for feeding, and hemolymph that serves as a rough equivalent to blood in insects.
		By contrast, the solid shell of the rostrum is comprised entirely of cuticle, which can be thought of as a laminate composite consisting of various arrangements of chitin fibers embedded in a protein matrix (see \ref{sec:microstructure}).

	These modifications enable the snout to be flexed until straight, remaining within the elastic limits of the material, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure.
	Thus, the flexibility of the rostrum appears to be derived exclusively through modification of the composite architecture and fiber arrangement in the exoskeleton.
	Support for this hypothesis has come from three lines of evidence: first, examination of the cuticle microstructure across the length of the snout has revealed modifications to the composite structure of the rostrum; second, tensile testing of the structure has demonstrated that the mechanical strength of the cuticle components are consistent along the length of the structure among species; and, third, fatigue testing has shown that a highly curved rostrum is capable of flexing hundreds of thousands of times without damage to the structure.
	We additionally report on the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	To our knowledge, this is the first time such modifications have been reported for enhancing structural elasticity in the insect exoskeleton.

>>>>

		As a weevil (snout beetle), members of the genus \textit{Curculio} are typified by the presence of a highly elongate structure on the head, called the rostrum (snout). 
		This structure is a hollow, cylindrical extension of the exoskeleton of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts. 
		The space inside of the rostrum contains the esophagus, various muscles and tendons used for feeding, and hemolymph that serves as a rough equivalent to blood in insects.
		By contrast, the solid shell of the rostrum is comprised entirely of cuticle, which can be considered a laminate composite consisting of various arrangements of chitin fibers embedded in a protein matrix (see \ref{sec:microstructure}).
		We have found that the composite profile of the rostrum is strongly differentiated from the head capsule and other body parts, with modification of both the relative layer thicknesses and fiber orientation angles of cuticle regions (viz. exocuticle and endocuticle), which we describe in detail below.

	These modifications enable the snout to be flexed until straight while remaining within the elastic limits of the material and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility of the rostrum appears to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	Support for this hypothesis has come from three lines of evidence: first, examination of the cuticle microstructure across the length of the snout has revealed consistent modification to the composite structure of the rostrum among \textit{Curculio} species; second, tensile testing of the structure has demonstrated that the mechanical strength of the cuticle components are consistent along the length of the structure and between species; and, third, fatigue testing has shown that a highly curved rostrum is capable of flexing hundreds of thousands of times without damage to the structure, and is apparently elastic.
	We additionally report on the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	To our knowledge, this is the first time such modifications have been reported for enhancing structural elasticity in the insect exoskeleton.
